Inferring the distribution and rate of Earth-like exoplanets \\ from noisy individual-planet inferences

### 2014-05-15 document/ms.tex
some notes about the median transit probability

The detection efficiency also depends on the geometric transit probability
$R_\star/a$.
Since we're modeling the distribution in the period--radius plane, we need to
compute the transit probability marginalized over stellar radius and mass.
This marginalized distribution scales only with the period of the orbit as
$\propto \period^{-2/3}$.
In theory, this marginalization should be over the true distribution of these
parameters in the selected stellar catalog but we'll approximate it by
the empirical distribution; a reasonable approximation given the size of the
dataset.
At a period of 10 days, the median transit probability in the selected sample
of stars is $5\%$ so we model the transit probability\footnote{We're using the
letter $Q$ to indicate probabilities since we're already using $P$ to mean
period.} as a function of period as
\begin{eqnarray}
\transitprob (\period) &=&
    0.05\,\left[\frac{\period}{10\,\mathrm{days}}\right]^{-2/3} \quad.
\end{eqnarray}

>>>>

The detection efficiency also depends on the geometric transit probability
$R_\star/a$.
Since we're modeling the distribution in the period--radius plane, we need to
compute the transit probability marginalized over stellar radius and mass.
This marginalized distribution scales only with the period of the orbit as
$\propto \period^{-2/3}$.
In theory, this marginalization should be over the true distribution of these
parameters in the selected stellar catalog but we'll approximate it by
the empirical distribution; a reasonable approximation given the size of the
dataset.
At a period of 10 days, the median transit probability in the selected sample
of stars is $5\%$ so we model the transit probability\footnote{We're using the
letter $Q$ to indicate probabilities since we're already using $P$ to mean
period.} as a function of period as
\begin{eqnarray}
\transitprob (\period) &=&
    0.05\,\left[\frac{\period}{10\,\mathrm{days}}\right]^{-2/3} \quad.
\end{eqnarray}
This expression is clearly only valid for $\period \gtrsim 1.4\,\mathrm{days}$
but the dataset that we're using (\citealt{petigura}) explicitly only includes
periods longer than five days so this isn't a problem.
It's also worth noting that we're using the \emph{median} transit probability
(instead of the mean) because it is a more robust estimator in the presence of
outliers.
In our experiments, the results do not seem to be very sensitive to this
choice.
\dfmtodo{Is there any rough scaling that is obvious?}
